\documentclass{scrartcl}

\usepackage{polyglossia,graphicx}
\setdefaultlanguage{swedish}

\begin{document}

\title{Group reflection week 3}
\author{Group Joy}
\date{\today}
\maketitle

\section{Customer Value and Scope}

\subsection{The chosen scope of the application under development including the priority of features and for whom you are creating value} 

Our plan is still to create an interactive map over Sweden, there you can show statistics in a form of a heatmap.
The goal is to highlight differences in different parts of the country.
The data will come from one or multiple government agencies.

This was our initial plan, and we haven't had a change of mind.

\subsection{The success criteria for the team in terms of what you want to achieve within the project (this can include the application, but also your learning outcomes, your teamwork, or your effort)}

The success criteria is simply to deliver a decent product and all feel that we have contributed and have had a pleasant working experience with each other. 

As of right now we are on track to deliver a product and enjoying our cooperation. We have considered that the project might be a bit to small for everyone to meaningfully contribute each week. 

We plan to keep up the pleasant work experience by opening our meetings with a quick check in so that everyone is feeling all right. We also plan to do a bit of team building. As for the issue with the project we figure that everyone should consider what they want to do on this project, we will then have to adjust the project accordingly, perhaps focusing on increasing functionality of the core application once usable.

\subsection{Your user stories in terms of using a standard pattern, acceptance criteria, task breakdown and effort estimation and how this influenced the way you worked and created value}

We currently create intentionally small user stories with the goal of making them easy to finish.
We haven't felt a need to break the user stories down into smaller tasks because the stories is already enough small to be manageable.
Each user story have had one or more acceptance criteria, with some non-code related being the exceptions.
The acceptance criteria has been primarily used as a formality, and haven't helped us in our work.
We think that we've used our group meetings as a place to check with the other team members if our work is ``finished''.
We've initiated each new sprint with a meeting on Mondays estimating the user stories that we need to take next, and then stopping when we had estimated enough user stories to fill our week.

We are pleased with how we've written small enough user stories that we don't need to split them further.
We could definitely write our acceptance criteria much more detailed, so that we don't need to talk to people to know that we're finished with a story.
There will still be some integration work, but that will be just small details compared to the other work.
Regarding the estimation we think that if we write more clear acceptance criteria, and clearly define our user stories, it will be much easier to estimate.
Then we can take a meeting and just estimate all stories that is currently in the backlog.


\subsection{KPIs}

We currently haven't choosen any KPI for how we should work.
The reason is that we've focused on getting up and running with the project, and build up the kanban board.

We should have three KPIs at the end of next week, preferable at the start of the week so we have something to measure.

To get there our scrum master and PO will be select at least one KPI before the next sprint.

\section{Application of Scrum}

\subsection{The roles you have used within the team and their impact on your work}

We've just the scrum master and the product owner as formal roles in our team.
We've a rolling schedule there everyone tests to be the scrum master and the PO one time.
The other people in the group focus on the programming part rest of the week.
The programming part is split into the front- and backend.
So get kinda an informal role as a ``front-end'' or ``back-end` developer for a week.

We currently don't have any other plans for roles in our group.

\end{document}