\documentclass[]{article}
\begin{document}
\textbf{\huge{LV5} Erik Waser}

\begin{itemize}
    \item \textbf{What do I want to learn or understand better?} \newline
    I want to learn more about the d3 library. I haven't had the time or opportunity to look into it and think that doing so would enable me to help out in adding functionality to our product. 
    I know that I have a dificult time learning by reading so I plan to speak with my group to see if someone with a better grasp of the library might be willing to sit down with me and show me. 
    
    
    \item \textbf{How can I help someone else, or the entire team, to learn something new?} \newline
    I don't think I can add a lot of knowledge to the others as far as technical knowhow and skill is concerned. I think that my biggest contribution to this project has been creating some emblance of order around our meetings and group dynamics. But i suppose that a lot of that is in order now. I do intend to keep holding the meetings and making sure that everyone has a pleasant experience while working in this group. 
    
    \item \textbf{What is my contribution towards the team’s use of Scrum?} \newline
    I typically hold the meetings and make sure that we get somewhere when discussing the project and what to do next. I created the framework for our meetings as well and take notes to make sure everyone knows what waas said and what was decided.
    
    \item \textbf{What is my contribution towards the team’s deliveries?} \newline
    Honestly, I've had to work a lot during this course, this combined with the fact that we have had issues with people not pushing their work to github has meant that I have felt like I've been behind from the start. I don't have the same amount of time to spend on the project and then when i sit down I'm not sure where we stand and what's happening in the project. Because of this I have been strugling to contribute anything. This is something I recently brought up to the group and they seemed to be understanding. I think that getting to learn D3 better will help me not only to produce something but also to raise my confidence.
    
 
\end{itemize}

\end{document}

