\documentclass[]{article}
\begin{document}
\textbf{\huge{LV5}}

\begin{itemize}
    \item \textbf{What do I want to learn or understand better?} \newline
    I want to learn more about how to use the D3 library, specifically how to make use of our data to display values. I think this shouldn't be to hard in the future due to Kresimirs previous work. It sets a foundation to build upon, and I think as long as i put the effort in there shouldn't be too much trouble.
    
    \item \textbf{How can I help someone else, or the entire team, to learn something new?} \newline
    Kresimir had the idea to implement a live team editor in our development. This is something I feel would help ease development, as some of us are working in the same document. I will look into the possibilities of this. Another thing I've noticed is that me, and some other members work more efficient when we're working in groups, rather than individually. Whilst working in groups, we can share our knowledge with each other and ask each other questions about the development.
    
    \item \textbf{What is my contribution towards the team’s use of Scrum?} \newline
    Always in the meetings, I am active in the discussion of which User Stories to focus on for the week,as well as which ones we should drop completely to make sure we finish on time etc.
    
    \item \textbf{What is my contribution towards the team’s deliveries?} \newline
    This week I did little to any contribution. I made some code for how we could display the data as a heatmap, but ultimately Kresimir came with a better solution which we ended up settling for.
    

 
 
\end{itemize}

\end{document}

