\documentclass[]{article}
\begin{document}
\textbf{\huge{LV7} Erik Waser}

\begin{itemize}
    \item \textbf{What do I want to learn or understand better?} \newline
    I want to learn exactly how the project functions better than i do right now. If our meetings are anything to go by I am one of the people who talk the most. This means that I will likely be leading at least a part of our presentation. For this I want to learn a bit more about the server we have running in the back-end. Last week I worked with Kresimir and it was actually really helpful. So in preperation for the presentation i was thinking that I could work with some or all of the others to make sure that i learned it and use the way it is explained to me as a basis for the presentation. This will require coordination, something that we have admittedly had problems with in the past. But I think we can do it.
    
    \item \textbf{How can I help someone else, or the entire team, to learn something new?} \newline
    I have had a week with a unexpected amount of work to do aside from this course. That means i have not been taking part in the meetings and discussions as much as the others. When i have talked with the others I hve understood that the meetings have been a bit all over the place and unfocused. That is why i made the agenda, to focus our meetings. 
    
    
    \item \textbf{What is my contribution towards the team’s use of Scrum?} \newline
    I pushed the issue of us having to few KPIs and not using them so now we have them down. We have shirt sizes, comparing an estimated velocity to actual velocity and comparing user satisfaction in the same way, by giving each user story a UP or user point based on how valuable it is for the user. 
    
    \item \textbf{What is my contribution towards the team’s deliveries?} \newline
    As I've said in previous reflections I have not contributed as much to the actual code as the others. I have written many of our reflections but that was with the input and help of the others. However along with Albin i realized that because I'm less familiar with the code I am in a good position to document and explain the code. So I've spent some time writing some documentation and making sure it is understandable for someone who might not be comfortable fith javasript or the project itself. 
    
\end{itemize}

\end{document}

