\documentclass[]{article}
\begin{document}
\textbf{\large{LV5 - Max}}

\begin{itemize}
    \item \textbf{What do I want to learn or understand better?} \newline
    Approaching the end of the course, I feel it is time to set an end-goal for our application. This is crucial for everyone in order to select the next task. I need to work a little bit more on understanding our d3-method for data importing. Heading into next week, my learning goals depend on what work I am assigned to. But it will probably be adding some more CSS to make the website more user-friendly, and perhaps also adding more options for statistics using the same techniques as I did this week.
    
    \item \textbf{How can I help someone else, or the entire team, to learn something new?} \newline
    The code I am about to push includes some new techniques which at least I did not understand immediately. I need to structure up the project and comment it properly before pushing to make it easy to digest.
    
    \item \textbf{What is my contribution towards the team’s use of Scrum?} \newline
    I make sure that a short meeting is held by the middle of each week for everyone to check in on each ones work. Someone may for instance be stuck on a problem or need the others opinion on a design choice, etc. This insures that proper communication is held more often then once a week, and helps everyone get more out of each sprint.  
    
    \item \textbf{What is my contribution towards the team’s deliveries?} \newline
    This week I designed a method for data-importing from csv, and added a selector with options of statistics which now get displayed properly when hoovering on the map. I should be able get the colors change properly before Monday, thus reaching my goal of this week. 
 
    

 
 
\end{itemize}

\end{document}